---
title: "Sample Selection"
format: html
editor: visual
execute:
  echo: false
  warning: false
  message: false
---

```{r}
source("sample_selection_core.R")
```

# Sampling Frame Construction

The sampling frame was built from 2020 Census tract and block-group files for Detroit, Michigan. Census tracts are the primary sampling units (PSUs), block groups are the secondary sampling units (SSUs), and persons are the ultimate elements.

```{r}
tibble(
  n_tracts_raw = n_distinct(tract$Tract),
  n_tracts_frame = nrow(tract_frame),
  n_bgs_frame = nrow(bg_frame)
)
```

## Tract Flags and Screening Rules

```{r}
tract %>%
  summarise(
    zero_adult_population = sum(zero_pop_flag, na.rm = TRUE),
    fewer_than_two_bgs = sum(lt2_bg_flag, na.rm = TRUE),
    small_adult_population = sum(small_age18p_flag, na.rm = TRUE)
  )
```

# Respondent Targets and Equal-Rate Check

```{r}
resp_targets
```

```{r}
same_rate_check
```

# Measure of Size

A response-rate-adjusted measure of size was used:

$$
MOS_i = \frac{N_{i,18-34}}{0.35} + \frac{N_{i,35-49}}{0.45} + \frac{N_{i,50-64}}{0.50} + \frac{N_{i,65+}}{0.65}
$$

```{r}
tract_frame %>%
  summarise(
    min_MOS = min(MOS, na.rm = TRUE),
    q1_MOS = quantile(MOS, 0.25, na.rm = TRUE),
    median_MOS = median(MOS, na.rm = TRUE),
    mean_MOS = mean(MOS, na.rm = TRUE),
    q3_MOS = quantile(MOS, 0.75, na.rm = TRUE),
    max_MOS = max(MOS, na.rm = TRUE)
  )
```

# PSU and SSU Selection

## Selected Tracts

```{r}
tract_sample %>%
  select(Tract, NAME, n_bg, age18p, MOS, pik1, psu_weight)
```

## Selected Block Groups

```{r}
bg_sample %>%
  select(Tract, BlockGroup, NAME, age18p, MOS, pik2, ssu_weight)
```

# Person-Level Allocation

```{r}
bg_sample %>%
  select(
    Tract, BlockGroup,
    age18_34, age35_49, age50_64, age65p,
    n18_34, n35_49, n50_64, n65p,
    f18_34, f35_49, f50_64, f65p
  )
```

```{r}
bg_sample %>%
  summarise(
    total_n18_34 = sum(n18_34, na.rm = TRUE),
    total_n35_49 = sum(n35_49, na.rm = TRUE),
    total_n50_64 = sum(n50_64, na.rm = TRUE),
    total_n65p = sum(n65p, na.rm = TRUE),
    avg_workload = mean(n18_34 + n35_49 + n50_64 + n65p, na.rm = TRUE),
    min_workload = min(n18_34 + n35_49 + n50_64 + n65p, na.rm = TRUE),
    max_workload = max(n18_34 + n35_49 + n50_64 + n65p, na.rm = TRUE)
  )
```

# Weights

```{r}
cv_weights
```

# Exported Files

Running `sample_selection_core.R` writes these CSV files:

-   `frame_tract_out_CV.csv`
-   `frame_bg_out_CV.csv`
-   `sample_out_CV.csv`
-   `frame_codebook_CV.csv`
-   `sample_codebook_CV.csv`

# Codebook: Frame Files

```{r}
frame_codebook
```

# Codebook: Sample File

```{r}
sample_codebook
```
